Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-06-22 paper.tex
Spelling

\section{Discussion}
It was anticipated that this problem would be easy to model. This naivety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
team's communications, it was also a constraint (the \emph{regular} constraint).

>>>>

\section{Discussion}
It was anticipated that this problem would be easy to model. This na{\"\i}vety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This na{\"\i}vety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
team's communications, it was also a constraint (the \emph{regular} constraint).
